Reproducible Research - Peer Assessment 1
======================================

## Loading and Preprocessing the data

Get the data and view structure and summary of data

```{r echo=TRUE}
activity <- read.csv("activity.csv")
str(activity)
summary(activity)
```

What is the mean number of steps taken per day?

``` {r echo=TRUE}
hist(activity$steps[!is.na(activity$steps)])
mean(activity$steps, na.rm=TRUE)
median(activity$steps, na.rm=TRUE)
```

What is the average daily activity pattern?

install required packages

```{r echo=FALSE}
install.packages("ggplot2", repos="http://cran.rstudio.com/")
install.packages("reshape", repos="http://cran.rstudio.com/")
library(ggplot2)
library(reshape)
````

Make time series plot of 5 minute  
interval (x-axis) and the average  
number of steps taken, averaged  
across all days (y-axis)

```{r echo=TRUE}
ac <- activity[,c(1,3)]
md <- melt(ac, id="interval", measured="steps")
ct <- cast(md, interval ~ variable, fun.aggregate = mean, na.rm = TRUE)
graph <- ggplot(ct, aes(interval, steps))
graph + geom_line()
```

which 5 minute interval, on average across all the days  
in the dataset, contains the maximum number of steps?

```{r echo=TRUE}
ct[order(-ct$steps),][1,"interval"]
```

Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r echo=TRUE}
for( i in 1:length(activity2$interval) ) {    
    if ( is.na(activity2$steps[i]) ) {
        activity2$steps[i] <- ct$steps[ct$interval == activity2$interval[i]]
    }     
}
```


